Analysis2

### 2023-10-27 Lahman Analysis/Rough Analysis 2/Analysis2.qmd
Add new model using stolen bases
Added stolen bases to a model, focusing on individual players rather than total stolen bases by age.

```{r}
fit23b <- stan(
  file = "HR24.stan",
  data = data24,
  iter = 500
)
```

@@

>>>>

```{r}
fit24 <- stan(
  file = "HR24.stan",
  data = data24,
  iter = 2000
)
```

@@

```{r}
summary(fit24)$summary
```
```{r}
plot(fit24, pars = c("beta1", "c"))
```

### Another try with SB

Let's try a new version of the model above that separates players by SB as well as age.

```{r}
sum_all_years_SB <- Batting %>% group_by(yearID, Age, SB) %>%
  summarize(HR = sum(HR), AB = sum(AB))
```

```{r}
data24b <- list(
  N = nrow(sum_all_years_SB),
  n_year = n_distinct(sum_all_years_SB$yearID),
  AB = sum_all_years_SB %>% pull(AB),
  HR = sum_all_years_SB %>% pull(HR),
  Year = sum_all_years_SB %>% pull(yearID) -1972,
  Age = sum_all_years_SB %>% pull(Age) -30,
  SB = sum_all_years_SB %>% pull(SB)
)
```

```{r}
fit24b <- stan(
  file = "HR24b.stan",
  data = data24b,
  iter = 500
)
```
```{r}
print(fit24b)
```
```{r}
plot(fit24b, pars = "b")
```
```{r}
plot(fit24b, pars = c("beta1", "c"))
```

```{r}
Batting_summary_SB <- Batting %>% group_by(SB) %>%
  summarize(HR = sum(HR), AB = sum(AB)) %>%
  mutate(prop = HR / AB, se = sqrt(prop*(1-prop)/AB))

ggplot(data = Batting_summary_SB) +
  geom_pointrange(mapping = aes(x = SB, y = prop, ymin = prop - se,
                                ymax = prop + se))
```
